Cryptanalysis of \MORUS

### 2018-05-10 morusAC_07_IniFin.tex
last typo

\subsubsection{Remarks.}
The matching state does not have te be a border of a step. It can be defined on a border of a round (or even some complicated way). We did not find the extension of the number of attacked steps even with this way.

>>>>

\subsubsection{Remarks.}
The matching state does not have to be a border of a step. It can be defined on a border of a round, or even in some more complicated way. We did not find the extension of the number of attacked steps even with this way.
